Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-11-26 manuscript.tex
20161126

\textcolor{red}{In the aforementioned controller design, signum functions in inputs lead to chattering phenomena, which may cause adverse unmodeled dynamics to ruin the control system. Herein, we adopt the boundary layer technique, which has been widely used in engineering applications~\cite{Hwang1996sliding,In2000Robust,Chen2005}, to reduce chattering through replacing $\rm{sign}\it{(x)}$ by $\rm{sat}\it{(x/\nu)}$, where

@@

and $\nu$ is the boundary layer thickness. However, the cost of using boundary layer in sliding mode controller is that the asymptotic stability of proposed method can not be guaranteed. Hence we proceed to analyze the bounded stability in the following theorem.

@@

$\bm z$ is the position vector that describes the distances of system states in the boundary layer from $\bm S_{r2}=0$, and $\dot{\bm z}$ is the velocity vector correspondingly. It is obvious that $\bm z$ is bounded and has $\Vert\bm z\Vert\le\Vert\bm\nu\Vert$, where $\bm\nu=(\nu_1,\nu_2,\nu_3)^T,\nu_1=\nu_2=\nu_3\ll 1$ is a constant vector denoting the boundary layer thicknesses for the three channels. Since all the inputs are bounded, it is reasonable to assume that $\dot{\bm z}$ is bounded with $\Vert\dot{\bm z}\Vert\le \bar z$. $\eta$ is defined as a state dependent positive parameter that depicts the relation $\Vert\bm S_{q1}\Vert=\eta\Vert\bm S_{q2}\Vert$, for all $\Vert\bm S_{q1}\Vert\neq 0$, $0<\eta<1$, when $\Vert\bm S_{q1}\Vert= 0$, $\eta$ especially values as $\eta = 1$.

>>>>

\textcolor{red}{In the aforementioned controller design, signum functions in inputs lead to chattering phenomena, which may cause adverse unmodeled dynamics to ruin the control system. Herein, we adopt the boundary layer technique, which has been widely used in engineering applications~\cite{Youndg1999A,Hwang1996sliding,In2000Robust,Chen2005,Yu2009sliding,Jin2009Practical,Al2004sliding}, to reduce chattering through replacing $\rm{sign}\it{(x)}$ by $\rm{sat}\it{(x/\nu)}$, where

@@

and $2\nu$ is the boundary layer thickness. However, the cost of using boundary layer in sliding mode controller is that the asymptotic stability of proposed method can not be guaranteed. Hence we proceed to analyze the bounded stability in the following theorem.

@@

$\bm z$ is the position vector that describes the distances of system states in the boundary layer from $\bm S_{r2}=0$, and $\dot{\bm z}$ is the velocity vector correspondingly. It is obvious that $\bm z$ is bounded and has $\Vert\bm z\Vert\le\Vert\bm\nu\Vert$, where $\bm\nu$ is a constant vector denoting the boundary layer thicknesses. Since all the inputs are bounded, it is reasonable to assume that $\dot{\bm z}$ is bounded with $\Vert\dot{\bm z}\Vert\le \bar z$. $\eta$ is defined as a state dependent positive parameter that depicts the relation $\Vert\bm S_{q1}\Vert=\eta\Vert\bm S_{q2}\Vert$, for all $\Vert\bm S_{q1}\Vert\neq 0$, $0<\eta<1$, when $\Vert\bm S_{q1}\Vert= 0$, $\eta$ especially values as $\eta = 1$.
